Concurrent Programming in Harmony

### 2021-01-23 book/paper.tex
Latest
Book updated to use where

\newcommand{\harmonylink}[1]{%
[\href{https://www.cs.cornell.edu/home/rvr/harmony/#1}{\underline{#1}}]%
}

\newcommand{\harmonyref}[2]{%
\href{https://www.cs.cornell.edu/home/rvr/harmony/output/#1}{\underline{#2}}%
}

@@

Harmony also supports \emph{set comprehension}.  In its simplest form,
\texttt{\{ f($v$) for $v$ in $s$ \}} returns a set that is constructed
by applying \texttt{f} to all elements in $s$ (where $s$ is a set or
a list).
This is known as \emph{mapping}.  But set comprehension is much more
powerful and can include joining multiple sets (using nested for
loops) and filtering (using the \texttt{such that} keywords).

@@

Harmony supports nesting and filtering in \texttt{for loops}.
For example:
\begin{code}
\texttt{for} $i$ in \{ 1..10 \}
\texttt{for} $j$ in \{ 1..10 \}
\texttt{such that} $i < j$: ...
\end{code}

Harmony also supports set, list, and dictionary comprehensions.
\index{comprehensions}%
Set and list comprehensions are similar to Python, except that filtering uses
the keywords \texttt{such that} instead of \texttt{if}.
Dictionary comprehensions are a little different.
The dictionary comprehension \texttt{dict}\{ f($i$) \texttt{for} $i$ \texttt{in} $I$ \}
creates a dictionary of $i$:f($i$) entries.

>>>>

\newcommand{\harmonylink}[1]{%
[\href{https://harmony.cs.cornell.edu/#1}{\underline{#1}}]%
}

\newcommand{\harmonyref}[2]{%
\href{https://harmony.cs.cornell.edu/output/#1}{\underline{#2}}%
}

@@

Harmony also supports \emph{set comprehension}.  In its simplest form,
\texttt{\{ f($v$) for $v$ in $s$ \}} returns a set that is constructed
by applying \texttt{f} to all elements in $s$ (where $s$ is a set or
a list).
This is known as \emph{mapping}.  But set comprehension is much more
powerful and can include joining multiple sets (using nested for
loops) and filtering (using the \texttt{where} keyword).

@@

Harmony supports nesting and filtering in \texttt{for loops}.
For example:
\begin{code}
\texttt{for} $i$ in \{ 1..10 \}
\texttt{for} $j$ in \{ 1..10 \}
\texttt{where} $i < j$: ...
\end{code}

Harmony also supports set, list, and dictionary comprehensions.
\index{comprehensions}%
Set and list comprehensions are similar to Python, except that filtering uses
the keyword \texttt{where} instead of \texttt{if}.
Dictionary comprehensions are a little different.
The dictionary comprehension \texttt{dict}\{ f($i$) \texttt{for} $i$ \texttt{in} $I$ \}
creates a dictionary of $i$:f($i$) entries.
